---
title: "Capacity Paper Figures"
author: "RegLab"
date: "3/7/2021"
output: html_document
---


## Setup imports
```{r, warning=FALSE}
# Imports
library(tidyverse)
library(lubridate)
library(cowplot)
library(msir)
```


## Source capacity paper variables
```{r}
source("scripts/capacity_paper_variables-backfill.R")
```


# Place stats

```{r}
readRDS(paste0(data_path, "scc_places_df.rds")) %>% 
  group_by(type) %>% 
  summarize(n())
```


# Occupancy Ratio Plots

## Load 2019 and 2020 data
```{r}
scc_preprocessed_2019_df <- 
  readRDS(
    paste0(data_path, "scc_preprocessed_2019_df.rds")
  )

scc_preprocessed_2020_df <- 
  readRDS(
    paste0(data_path, "scc_preprocessed_2020_df.rds")
  )
```


## Filter dates and sectors and bind dataframes.
```{r}
scc_hourly_post_2019_df <-  
  scc_preprocessed_2019_df %>% 
  filter(
    date >= ymd(post_2019_start_date) 
    & date <= ymd(post_2019_end_date)
  ) %>% 
  mutate(
    date_bin = paste0(post_2019_start_date, " to ", post_2019_end_date),
    period = "After",
    year = 2019
  )

scc_hourly_post_2020_df <-  
  scc_preprocessed_2020_df %>% 
  filter(
    date >= ymd(post_2020_start_date) 
    & date <= ymd(post_2020_end_date)
  ) %>% 
  mutate(
    date_bin = paste0(post_2020_start_date, " to ", post_2020_end_date),
    period = "After",
    year = 2020
  )

scc_hourly_pre_2019_df <-  
  scc_preprocessed_2019_df %>% 
  filter(
    date >= ymd(pre_2019_start_date) 
    & date <= ymd(pre_2019_end_date)
  ) %>% 
  mutate(
    date_bin = paste0(pre_2019_start_date, " to ", pre_2019_end_date),
    period = "Before",
    year = 2019
  )

scc_hourly_pre_2020_df <-  
  scc_preprocessed_2020_df %>% 
  filter(
    date >= ymd(pre_2020_start_date) 
    & date <= ymd(pre_2020_end_date)
  ) %>% 
  mutate(
    date_bin = paste0(pre_2020_start_date, " to ", pre_2020_end_date),
    period = "Before",
    year = 2020
  )

scc_hourly_df <- 
  rbind(
    scc_hourly_pre_2019_df,
    scc_hourly_post_2019_df,
    scc_hourly_pre_2020_df,
    scc_hourly_post_2020_df
  )

scc_hourly_df <- 
  scc_hourly_df %>% 
  select(-sector) %>% 
  rename(sector = type)

scc_hourly_df$period_f <- 
  factor(
    scc_hourly_df$period, 
    levels = c('Before', 'After'),
    labels = c('Before Dec. 6', 'After Dec. 7')
  )
```


## Filter open hours and occupancy ratios outside of (0, 1) and religious organizations
```{r}
scc_hourly_clean_df <- 
  scc_hourly_df %>% 
  filter(is_open & occupancy_ratio > 0 & occupancy_ratio <= 1)

scc_hourly_clean_df$sector <- 
  factor(
    scc_hourly_clean_df$sector,
    levels = sector_factor_levels,
    labels = sector_factor_labels
  )
```


## Compute sector statistics for hours with occupancy above threshold
```{r}
over_threshold_labels <- 
  scc_hourly_clean_df %>% 
  mutate(
    over_threshold_20 = occupancy_ratio > 0.2,
  ) %>% 
  group_by(sector, date_bin, period_f, year) %>% 
  summarize(
    count_over_20 = sum(over_threshold_20),
    count_total = n()
  ) %>% 
  mutate(
    percent_over_20 = count_over_20 / count_total * 100
  ) %>% 
  select(
    sector, 
    date_bin,
    period_f,
    year,
    percent_over_20,
    count_total,
  ) %>% 
  left_join(
    data.frame(
      sector = factor(
        c("big_box", "grocery", "pharmacy"),
        levels = sector_factor_levels,
        labels = sector_factor_labels
      ),
      y_low  = c(2250, 5000, 2500)
    ),
    by = "sector"
  ) %>% 
  unite("period_sector", period_f, sector, remove = FALSE)

over_threshold_labels
```


## Plot histogram of occupancy ratio per hour
```{r}
mean(scc_hourly_clean_df$occupancy_ratio > 0.3)

or_hist_df <-
  scc_hourly_clean_df %>% 
  filter(occupancy_ratio <= 0.3) %>% 
  unite("period_sector", period_f, sector, remove = FALSE)

unique(or_hist_df$period_sector)
```


```{r}
GeomStepHist <- ggproto("GeomStepHist", GeomPath,
                        required_aes = c("x"),

                        draw_panel = function(data, panel_scales, coord, direction) {
                          data <- as.data.frame(data)[order(data$x), ]

                          n <- nrow(data)
                          i <- rep(1:n, each=2)
                          newdata <- rbind(
                            transform(data[1, ], x=x - width/2, y=0),
                            transform(data[i, ], x=c(rbind(data$x-data$width/2, data$x+data$width/2))),
                            transform(data[n, ], x=x + width/2, y=0)
                          )
                          rownames(newdata) <- NULL

                          GeomPath$draw_panel(newdata, panel_scales, coord)
                        }
)


geom_step_hist <- function(mapping = NULL, data = NULL, stat = "bin",
                           direction = "hv", position = "stack", na.rm = FALSE, 
                           show.legend = NA, inherit.aes = TRUE, ...) {
  layer(
    data = data,
    mapping = mapping,
    stat = stat,
    geom = GeomStepHist,
    position = position,
    show.legend = show.legend,
    inherit.aes = inherit.aes,
    params = list(
      direction = direction,
      na.rm = na.rm,
      ...
    )
  )
}
```



```{r}
hist_period_labels <- data.frame(
  period_f = rep(c("Before Dec. 6", "After Dec. 7"), 3),
  year = rep("2019", 6),
  x = rep(c(0.025, 0.035), 3),
  y = c(9000, 5500, 9000, 5000, 20500, 10000),
  sector = c("big_box", "big_box", "pharmacy", "pharmacy", "grocery", "grocery"),
  period_sector = c("Before Dec. 6_General Merchandise Stores", "After Dec. 7_General Merchandise Stores", "Before Dec. 6_Pharmacies", "After Dec. 7_Pharmacies", "Before Dec. 6_Grocery Stores", "After Dec. 7_Grocery Stores")
)

hist_period_labels$sector <- 
  factor(
    hist_period_labels$sector,
    levels = sector_factor_levels,
    labels = sector_factor_labels
  )

occupancy_ratio_hist <- 
  ggplot() +
    geom_histogram(
      data = or_hist_df %>% filter(period_f == "Before Dec. 6"),
      aes(x = occupancy_ratio, y = ..count.., fill = period_sector),
      bins = 40,
      position = "identity"
    ) +
    geom_step_hist(
      data = or_hist_df %>% filter(period_f == "After Dec. 7"),
      aes(x = occupancy_ratio, y = ..count.., color = period_sector),
      bins = 40, 
      position = "identity"
    ) +
    geom_vline(xintercept = 0.2, linetype = "dashed", color = "#212121") +
    geom_text(
      data = hist_period_labels,
      mapping = aes(x = x, y = y, label = period_f, color = period_sector, hjust = 0),
      size = 3
    ) +
    xlab("Fraction of maximum occupancy") + 
    ylab("Hours") +
    scale_y_continuous(breaks = scales::pretty_breaks(n = 2), labels = scales::comma) +
    facet_grid(
      sector ~ year, 
      scale = "free_y",
      labeller = labeller(sector = label_wrap_gen(15))
    ) + 
    theme_classic() +
    theme(
      legend.position = "none",
      #strip.text.y = element_text(angle = 0),
      strip.text.y = element_blank(),
      strip.background = element_blank()
    ) +
    scale_fill_manual(values = sector_period_colors) +
    scale_color_manual(values = sector_period_colors)

occupancy_ratio_hist
```


```{r}
hours_period_labels <- data.frame(
  period_f = rep(c("Before Dec. 6", "After Dec. 7"), 3),
  x = c(2019.25, 2019, 2019, 2019.25, 2019, 2019.25),
  y = c(44500, 41000, 42000, 50500, 82000, 97000),
  sector = c("General Merchandise Stores", "General Merchandise Stores", "Pharmacies", "Pharmacies", "Grocery Stores", "Grocery Stores"),
  period_sector = c("Before Dec. 6_General Merchandise Stores", "After Dec. 7_General Merchandise Stores", "Before Dec. 6_Pharmacies", "After Dec. 7_Pharmacies", "Before Dec. 6_Grocery Stores", "After Dec. 7_Grocery Stores")
)

hours_plot <- 
  over_threshold_labels %>% 
  ggplot() +
    geom_line(aes(x = year, y = count_total, color = period_sector)) +
    geom_point(aes(x = year, y = count_total, color = period_sector)) +
    geom_text(
      data = hours_period_labels,
      mapping = aes(x = x, y = y, label = period_f, color = period_sector, hjust = 0),
      size = 3
    ) +
    xlab("Year") + 
    ylab("Nonzero occupancy hours") +
    scale_x_continuous(breaks = c(2019, 2020)) +
    scale_y_continuous(breaks = scales::pretty_breaks(n = 2), labels = scales::comma) +
    facet_grid(
      rows = vars(sector), 
      scale = "free_y",
      labeller = labeller(sector = label_wrap_gen(15)) 
    ) + 
    theme_classic() +
    theme(
      legend.position = "none",
      strip.text.y = element_text(angle = 0),
      #strip.text.y = element_blank(),
      strip.background = element_blank()
    ) +
    scale_color_manual(values = sector_period_colors)

hours_plot
```


```{r}
ggsave(
  paste0(
    repo_path, "figures/", "figure_4.png"
  ),
  plot = plot_grid(
    occupancy_ratio_hist, 
    hours_plot, 
    labels = "auto",
    nrow = 1,
    rel_widths = c(2, 1.25)
  ),
  height = 3,
  width = 8
)
```


# Hourly distribution appendix figure

```{r}
or_hist_df <- scc_hourly_df

or_hist_df$sector <-
  factor(
    or_hist_df$sector,
    levels = sector_factor_levels,
    labels = sector_factor_labels
  )

or_hist_df <- 
  or_hist_df %>% 
  group_by(
    year,
    sector,
    hour,
    period_f,
  ) %>%
  summarize(avg_hourly_visits=mean(hourly_visits_smeared)) %>% 
  unite("period_sector",period_f,sector, remove=FALSE) 

hist_period_labels <- data.frame(
  period_f = rep(c("Before Dec. 6", "After Dec. 7"), 3),
  x = rep(c(1, 6), 3),
  y = c(120,140,18,21,17,20),
  year = rep("2019", 6),
  sector = c("big_box", "big_box", "pharmacy", "pharmacy", "grocery", "grocery"),
  period_sector = c("Before Dec. 6_General Merchandise Stores", "After Dec. 7_General Merchandise Stores", "Before Dec. 6_Pharmacies", "After Dec. 7_Pharmacies", "Before Dec. 6_Grocery Stores", "After Dec. 7_Grocery Stores")
)

hist_period_labels$sector <- 
  factor(
    hist_period_labels$sector,
    levels = sector_factor_levels,
    labels = sector_factor_labels
  )

hourly_visits_plot <- 
  ggplot() +
    geom_bar(
      data = or_hist_df %>% filter(period_f == "Before Dec. 6"),
      aes(x = hour, y = avg_hourly_visits, fill = period_sector), stat="identity"
    ) +
    geom_bar(
      data = or_hist_df %>% filter(period_f == "After Dec. 7"),
      aes(x = hour, y = avg_hourly_visits, color = period_sector, fill=NA), 
      stat="identity"
    ) +
    geom_text(
      data = hist_period_labels,
      mapping = aes(x = x, y = y, label = period_f, color = period_sector, hjust = 0),
      size = 3
    ) +
    xlab("Hour of the Day") + 
    ylab("Average Hourly Visits") +
    scale_y_continuous(breaks = scales::pretty_breaks(n = 3), labels = scales::comma) +
    facet_grid(
      sector ~ year, 
      scale = "free_y",
      labeller = labeller(sector = label_wrap_gen(15))
    ) + 
    theme_classic() +
    theme(
      legend.position = "none",
      strip.text.y = element_text(angle = 0),
      #strip.text.y = element_blank(),
      strip.background = element_blank()
    ) +
    scale_fill_manual(values = sector_period_colors) +
    scale_color_manual(values = sector_period_colors)

hourly_visits_plot

ggsave(
  paste0(
    repo_path, "figures/", "hourly_visits.png"
  ), 
  hourly_visits_plot, 
  width=7.5, 
  height=6
)
```



# Academic vs SCC capacity limit comparison

## Load capacity limit data
```{r}
scc_capacity_limit_df <- 
  readRDS(
    paste0(data_path, "scc_capacity_limit_df.rds")
)

scc_capacity_limit_df <- 
  scc_capacity_limit_df %>%
  rename(sector = type) 

scc_capacity_limit_df$sector <- 
  factor(
    scc_capacity_limit_df$sector,
    levels = sector_factor_levels,
    labels = sector_factor_labels
  )
```


## Create capacity limit table
```{r}
se <- function(x) sqrt(var(x)/length(x))

diff <- 
  scc_capacity_limit_df %>% 
  group_by(sector) %>% 
  filter(scc_capacity_limit > 0 & academic_capacity_limit > 0) %>% 
  summarize(
    mean_abs = mean(scc_capacity_limit - academic_capacity_limit),
    se_abs = se(scc_capacity_limit - academic_capacity_limit),
    mean_rel = mean((scc_capacity_limit - academic_capacity_limit) / academic_capacity_limit),
    se_rel = se((scc_capacity_limit - academic_capacity_limit) / academic_capacity_limit)
  )

diff
```


## Compute summary statistics for paper
```{r}
sum(scc_capacity_limit_df$scc_capacity_limit > 
    scc_capacity_limit_df$academic_capacity_limit) / nrow(scc_capacity_limit_df)
```


```{r}
scc_capacity_limit_df %>% 
  group_by(sector) %>% 
  summarize(num = n()) %>% 
  inner_join(diff) %>% 
  weighted.mean(x = .$mean_rel, w = .$num)

# Percent of capacity limit for academic to match policy on average
1 / (scc_capacity_limit_df %>% 
  group_by(sector) %>% 
  summarize(num = n()) %>% 
  inner_join(diff) %>% 
  weighted.mean(x = .$mean_rel, w = .$num) + 1) * .2
```


## Create capacity limit scatterplot
```{r}
capacity_limit_hist <- 
  scc_capacity_limit_df %>% 
  ggplot(aes(x = academic_capacity_limit, y = scc_capacity_limit, color= sector)) +
    geom_point(alpha=0.8) +
    geom_abline(slope=1, intercept=0, linetype = "dashed", color = "#212121") +
    xlim(c(0, 675)) +
    ylim(c(0, 675)) +
    coord_fixed() +
    annotate(
      "text", x = 235, y = 225, 
      label = "Grocery Stores", 
      color = sector_colors["Grocery Stores"]
    ) +
    annotate(
      "text", x = 110, y = 290, 
      label = "Pharmacies", 
      color = sector_colors["Pharmacies"]
    ) +
    annotate(
      "text", x = 415, y = 650, 
      label = "General Merchandise\nStores", 
      color = sector_colors["General Merchandise Stores"]
    ) +
    xlab("Academic capacity limit (persons)") + 
    ylab("CA policy capacity limit (persons)") +
    theme_classic() +
    theme(
      aspect.ratio = 1,
      legend.position = "none"
    ) +
    scale_color_manual(values = sector_colors)

capacity_limit_hist

ggsave(
  paste0(
    repo_path, "figures/", "capacity_limit_scatterplot.pdf"
  ),
  plot = capacity_limit_hist,
  height = 3,
  width = 3
)
```


# Open Hours Histogram

## Load open hours data
```{r}
scc_sector_hourly_open_df <- readRDS(
  paste0(data_path, "scc_sector_hourly_open_df.rds")
)

scc_sector_hourly_open_df <- 
  scc_sector_hourly_open_df %>%
  rename(sector = type) %>% 
  filter(sector != "religious")

scc_sector_hourly_open_df$sector <- 
  factor(
    scc_sector_hourly_open_df$sector,
    levels = sector_factor_levels,
    labels = sector_factor_labels
  )
```


## Create open hour histogram
```{r}
open_hours_hist <- 
  scc_sector_hourly_open_df %>%  
  group_by(hour, sector) %>% 
  summarize(median_frac_open = quantile(frac_open, 0.5, rm.na = FALSE)) %>% 
  ggplot(., aes(x=hour, fill = sector)) +
    geom_bar(
      aes(y = median_frac_open), 
      #color = "#212121",
      stat = "identity", 
      position = position_dodge()
    ) +
    geom_hline(yintercept = 0.5, linetype ="dashed", color = "#212121") +
    annotate("text", x = 2.5, y = 0.1, label = "Grocery Stores", color = sector_colors["Grocery Stores"]) +
    annotate("text", x = 8.5, y = 0.95, label = "Pharmacies", color = sector_colors["Pharmacies"]) +
    annotate("text", x = 20, y = 1.03, label = "General Merchandise Stores", color = sector_colors["General Merchandise Stores"]) +
    scale_x_continuous(breaks = c(1, 5, 9, 13, 17, 21)) +
    ylab("Median fraction of stores open") +
    xlab("Hour") +
    theme_classic() +
    theme(legend.position = "none") +
    scale_fill_manual(values = sector_colors)

open_hours_hist

ggsave(
  paste0(
    repo_path, "figures/", "open_hours_hist.png"
  ),
  plot = open_hours_hist,
  height = 3.71,
  width = 6
)
```


# Assessor and Safegraph Square Footage Comparison  

## Load Safegraph and Assesor square footage data
```{r}
scc_parcels_df <- readRDS(
  paste0(repo_path, "data/scc_parcels_all_placekey.rds")
)

scc_places_df <- readRDS(
  paste0(repo_path, output_data_dir, "scc_places_df.rds")
)

scc_sqft_df <- 
  inner_join(
    scc_places_df %>% 
      mutate(
        placekey = paste0(substring(placekey, 1, 3), substring(placekey, 8))
      ),
    scc_parcels_df,
    by = "placekey"
  ) %>% 
  transmute(
    safegraph_place_id = safegraph_place_id,
    sector = type,
    safegraph_sq_ft = area_square_feet,
    assessor_sq_ft = SQ_FT,
    location_name = location_name,
    street_address = street_address,
    city = city,
    STREET_NUM = STREET_NUM,
    ADDR = ADDR,
    CITY = CITY
  ) 

scc_sqft_df$sector <- 
  factor(
    scc_sqft_df$sector,
    levels = sector_factor_levels,
    labels = sector_factor_labels
  )

scc_sqft_df %>% 
  group_by(sector) %>% 
  summarize(n())
```


## Create scatterplot of square footage reported by both sources
```{r}
sqft_scatterplot <- 
  scc_sqft_df %>% 
  filter(sector != "religious") %>% 
  ggplot(aes(x = safegraph_sq_ft, y = assessor_sq_ft, color = sector)) +
    geom_point(alpha= 0.8) +
    geom_abline(slope = 1, intercept = 0, linetype = "dashed", color = "#212121") +
    annotate("text", x = 36000, y = 98000, label = "Grocery Stores", color = sector_colors["Grocery Stores"]) +
    annotate("text", x = 50000, y = 130954, label = "Pharmacies", color = sector_colors["Pharmacies"]) +
    annotate("text", x = 140257, y = 52800, label = "General Merchandise Stores", color = sector_colors["General Merchandise Stores"]) +
    xlim(0, 200000) +
    ylim(0, 200000) +
    ylab(bquote("SCC Assessor area" ~ (ft^2))) +
    xlab(bquote("Safegraph area" ~ (ft^2))) +
    theme_classic() +
    theme(aspect.ratio = 1) +
    theme(legend.position = "none") +
    scale_color_manual(values = sector_colors)

sqft_scatterplot

ggsave(
  paste0(
    repo_path, "figures/", "sqft_scatterplot.png"
  ),
  plot = sqft_scatterplot,
  height = 4,
  width = 4
)
```


# Mobility case correlation plots

## Load dataframes
```{r}
lagged_analysis_data_df <-   
  readRDS(paste0(repo_path, data_dir, "lagged_analysis_data_df.rds"))

lagged_analysis_data_df$county <- 
  factor(
    lagged_analysis_data_df$county,
    levels = county_factor_levels
  )

correlations_df <- 
  readRDS(paste0(repo_path, data_dir, "correlations_df.rds"))

correlations_df$county <- 
  factor(
    correlations_df$county,
    levels = county_factor_levels
  )
```


```{r}
mobility_ratio_plot <- 
  lagged_analysis_data_df %>% 
  ungroup() %>% 
  select(county, date, mobility_dwell_ratio, mean_dwell_ratio_7) %>% 
  mutate(unlag_date = date - 11) %>% 
  ggplot(aes(color = county)) +
    geom_point(aes(x = unlag_date, y = mobility_dwell_ratio), size = 0.25) +
    geom_line(aes(x = unlag_date, y = mean_dwell_ratio_7)) +
    xlab("Date") +
    ylab("Mobility ratio") +
    theme_classic() +
    theme(legend.position = "bottom") +
    theme(legend.title = element_text(size = 8), legend.text = element_text(size = 8)) +
    scale_color_manual("County", values = county_colors)

mobility_ratio_plot

ggsave(
  paste0(
    repo_path, "figures/", "mobility_ratio.png"
  ),
  plot = mobility_ratio_plot,
  height = 3.71,
  width = 6
)
```


```{r}
lagged_weekday_data_df <-
  lagged_analysis_data_df %>% 
  ungroup() %>% 
  select(county, date, mobility_dwell_ratio, mean_dwell_ratio_7) %>% 
  mutate(
    unlag_date = date - 11,
    weekday = (as.integer(format(unlag_date, "%w")) + 6) %% 7,
    week = unlag_date - weekday
  ) %>% select(
    county,
    weekday,
    mobility_dwell_ratio,
    week
  )

mobility_weekday_df <-
  lagged_weekday_data_df %>% 
  filter(weekday <= 4) %>% 
  group_by(county, week) %>% 
  summarize(mean_mobility = mean(mobility_dwell_ratio)) %>% 
  ungroup()

mobility_weekend_df <-
  lagged_weekday_data_df %>% 
  filter(weekday >= 5) %>% 
  group_by(county, week) %>% 
  summarize(mean_mobility = mean(mobility_dwell_ratio)) %>% 
  ungroup()

min_exp = min(
  mobility_weekend_df$mean_mobility, 
  mobility_weekday_df$mean_mobility
) - 0.01
max_exp = max(
  mobility_weekend_df$mean_mobility, 
  mobility_weekday_df$mean_mobility
) + 0.01
```


```{r}
mobility_ratio_weekday_plot <- 
  mobility_weekday_df %>% 
  ggplot(aes(color = county)) +
    geom_point(aes(x = week, y = mean_mobility), size = 0.5) +
    geom_line(aes(x = week, y = mean_mobility)) +
    xlab("Week") +
    ylab("Average mobility ratio\n (weekdays)") +
    theme_classic() +
    theme(legend.position = "bottom") +
    theme(legend.title = element_text(size = 8), legend.text = element_text(size = 8)) +
    scale_color_manual("County", values = county_colors) +
    ylim(min_exp, max_exp) 

mobility_ratio_weekday_plot
```


```{r}
mobility_ratio_weekend_plot <- 
  mobility_weekend_df %>% 
  ggplot(aes(color = county)) +
    geom_point(aes(x = week, y = mean_mobility), size = 0.5) +
    geom_line(aes(x = week, y = mean_mobility)) +
    xlab("Week") +
    ylab("Average mobility ratio\n (weekends)") +
    theme_classic() +
    theme(legend.position = "bottom") +
    theme(legend.title = element_text(size = 8), legend.text = element_text(size = 8)) +
    scale_color_manual("County", values = county_colors) +
    ylim(min_exp, max_exp) 

mobility_ratio_weekend_plot
```


```{r}
legend = get_legend(mobility_ratio_weekday_plot)

prow <- plot_grid(
  mobility_ratio_weekday_plot + theme(legend.position = "none"), 
  mobility_ratio_weekend_plot + theme(legend.position = "none"), 
  labels = c('a', 'b')
)

mobility_week_days_ends_plot <- 
  plot_grid(prow, legend, ncol = 1, rel_heights = c(1, .2))

mobility_week_days_ends_plot

ggsave(
  paste0(
    repo_path, "figures/", "mobility_ratio_week_days_ends.png"
  ),
  plot = mobility_week_days_ends_plot,
  height = 3,
  width = 6.5
)
```



```{r}
case_growth_plot <- 
  lagged_analysis_data_df %>% 
  ggplot(aes(color = county)) +
    geom_point(aes(x = date, y = case_growth_alt), size = 0.5) +
    geom_smooth(aes(x = date, y = case_growth_alt), size = 0.5, span = 0.4, se = FALSE) +
    geom_hline(yintercept = 1, linetype="dashed", color = "#212121") + 
    ylim(0.75, 1.6) +
    xlab("Date") +
    ylab("Case growth ratio") +
    theme_classic() +
    theme(legend.position = "bottom") +
    theme(legend.title = element_text(size = 8), legend.text = element_text(size = 8)) +
    scale_color_manual("County", values = county_colors)

case_growth_plot

ggsave(
  paste0(
    repo_path, "figures/", "case_growth.png"
  ),
  plot = case_growth_plot,
  height = 3.71,
  width = 6
)
```


```{r}
county_loess_df <- NULL

for (curr_county in county_factor_levels) {
  curr_loess <- 
    correlations_df %>% 
    ungroup() %>% 
    filter(!is.na(dwell_corr_alt) & county == curr_county) %>% 
    loess.sd(
      x = .$date, 
      y = .$dwell_corr_alt,
      nsigma = 0.67,
      span = 0.5
    )
  
  curr_loess_df <- 
    data.frame(
      county = curr_county,
      x = zoo::as.Date(curr_loess$x),
      y = curr_loess$y, 
      lower = curr_loess$lower,
      upper = curr_loess$upper
    )
  
  county_loess_df <- rbind(county_loess_df, curr_loess_df)
}
```


```{r}
science_label_text <- data.frame(
  label = "Published\nscience", county = "Alameda", x = ymd("2020-04-21"), y = -0.825
)

county_correlation_plot <- 
  correlations_df %>%
  filter(date >= ymd("2020-04-01")) %>% 
  ungroup() %>% 
  ggplot() +
    geom_rect(
      aes(xmin = ymd("2020-04-07"), xmax = ymd("2020-05-07"), ymin = -Inf, ymax = Inf), 
      fill = "#EEEEEE", alpha = 0.1
    ) +
    geom_point(
      aes(x = date, y = dwell_corr_alt, color = county), 
      size = 0.25,
      alpha = 0.5
    ) +
    geom_ribbon(
      data = county_loess_df,
      aes(x = x, ymin = lower, ymax = upper, fill = county),
      alpha = 0.4
    ) +
    geom_line(
      data = county_loess_df,
      aes(x = x, y = y),
      color = "#FFFFFF",
      size = 1
    ) +
    geom_hline(yintercept = 0.0, linetype = "dashed", color = "#212121") +
    geom_text(data = science_label_text, aes(x = x, y = y, label = label), size = 3, color = "#212121") +
    #annotate("text", x = ymd("2020-04-21"), y = -0.825, label = "Published\nscience", county = "Alameda", size = 3, color = "#212121") +
    facet_wrap(~ county) + 
    xlab("Date") +
    ylab("Mobility-case growth correlation") +
    theme_classic() +
    theme(
      legend.position = "none",
      axis.text.x = element_text(angle = 45, hjust = 1),
      strip.background = element_blank()
    ) +
    scale_color_manual("County", values = county_colors) +
    scale_fill_manual("County", values = county_colors)

county_correlation_plot

ggsave(
  paste0(
    repo_path, "figures/", "smooth_correlation_county.png"
  ),
  plot = county_correlation_plot,
  height = 4.94,
  width = 8
)
```


```{r}
mean_loess <- 
  correlations_df %>% 
  ungroup() %>% 
  filter(!is.na(dwell_corr_alt)) %>% 
  loess.sd(
    x = .$date, 
    y = .$dwell_corr_alt,
    nsigma = 0.67,
    span = 0.4
  )

mean_loess_df <- 
  data.frame(
    x = zoo::as.Date(mean_loess$x),
    y = mean_loess$y, 
    lower = mean_loess$lower,
    upper = mean_loess$upper
  )
```


```{r}
overall_correlation_plot <- 
  correlations_df %>%
  filter(date >= ymd("2020-04-01")) %>% 
  ungroup() %>% 
  ggplot() +
    geom_rect(
      aes(xmin = ymd("2020-04-07"), xmax = ymd("2020-05-07"), ymin = -Inf, ymax = Inf), 
      fill = "#EEEEEE", alpha = 0.1
    ) +
    geom_point(
      aes(x = date, y = dwell_corr_alt, color = county), 
      size = 0.25,
      alpha = 0.5
    ) +
    geom_ribbon(
      data = mean_loess_df,
      aes(x = x, ymin = lower, ymax = upper),
      fill = "#d6566b", alpha = 0.4
    ) +
    geom_line(
      data = mean_loess_df,
      aes(x = x, y = y),
      color = "#FFFFFF",
      size = 1
    ) +
    geom_hline(yintercept = 0.0, linetype = "dashed", color = "#212121") +
    xlab("Date") +
    ylab("Mobility-case growth correlation") +
    theme_classic() +
    theme(
      legend.position = "bottom",
      legend.title = element_text(size = 8), 
      legend.text = element_text(size = 8)  
    ) +
    scale_color_manual("County", values = county_colors) +
    annotate("text", x = ymd("2020-04-21"), y = -0.825, label = "Published\nscience", size = 3, color = "#212121")

overall_correlation_plot

ggsave(
  paste0(
    repo_path, "figures/", "overall_correlation.pdf"
  ),
  plot = overall_correlation_plot,
  height = 3.71,
  width = 6
)
```

