---
title: "Capacity Paper Preprocessing"
author: "RegLab"
date: "3/7/2021"
output: html_document
---

## Setup imports
```{r, warning=FALSE}
# Imports
library(tidyverse)
library(lubridate)
library(jsonlite)
library(slider)
```


## Source capacity paper functions and variables
```{r}
source("scripts/capacity_paper_variables-backfill.R")
source("scripts/capacity_paper_functions-backfill.R")
```


# Preprocess SCC Places

## Load SafeGraph Core Places and square footage data
```{r}
sg_core_ca_df <- 
  readRDS(
    paste0(root_path, sg_poi_ca_dir, "core_poi-ca.rds")
  ) %>% 
  select(
    -c(
      "parent_safegraph_place_id", 
      "safegraph_brand_ids",
      "phone_number",
      "category_tags",
      "opened_on",
      "closed_on",
      "tracking_opened_since",
      "tracking_closed_since"
      )
    )
  
sg_sqft_df <- 
  readRDS(
    paste0(root_path, sg_poi_ca_dir, "may-june-august-sqft.rds")
  )

sector_ca_df <- filter_sector_df(sg_core_ca_df)
```


## Filter in scope place ids (does not need to be re-run frequently)
```{r}
in_scope_daily_df <- readRDS(
  paste0(data_path, "daily-patterns-bay/Santa Clara-daily-patterns-backfill.rds")
)

in_scope_place_ids <- 
  in_scope_daily_df %>% 
  filter(sector != "restaurant") %>% 
  .$safegraph_place_id %>% 
  unique()

saveRDS(
  in_scope_place_ids,
  paste0(data_path, "in_scope_place_ids.rds")
)

remove(in_scope_daily_df)
```


## Filter to in scope SCC places
```{r}
in_scope_place_ids <- 
  readRDS(
    paste0(data_path, "in_scope_place_ids.rds")
  )

scc_places_df <- 
  sector_ca_df %>% 
  filter(safegraph_place_id %in% in_scope_place_ids) %>% 
  left_join(
    sg_sqft_df %>% 
      select(-c("location_name", "polygon_class", "iso_country_code")) %>% 
      filter(safegraph_place_id %in% in_scope_place_ids),
    by = "safegraph_place_id"
  )

saveRDS(
  scc_places_df,
  paste0(data_path, "scc_places_df.rds")
)
```


## Explode open hours for SCC places
```{r}
scc_places_df %>% 
  filter(is.na(.$open_hours)) %>% 
  group_by(type) %>% 
  summarize(count=n())

scc_places_hourly_open_raw_df <- explode_open_hours(scc_places_df)

saveRDS(
  scc_places_hourly_open_raw_df,
  paste0(data_path, "scc_places_hourly_open_raw_df.rds")
)
```


## Determine average sector open hours for imputation
```{r}
scc_sector_hourly_open_df <- get_sector_open_hours(scc_places_hourly_open_raw_df, scc_places_df)

saveRDS(
  scc_sector_hourly_open_df,
  paste0(data_path, "scc_sector_hourly_open_df.rds")
)
```


## Impute missing place open hours
```{r}
scc_places_hourly_open_raw_df <- 
  readRDS(
    paste0(data_path, "scc_places_hourly_open_raw_df.rds")
  )

scc_sector_hourly_open_df <- 
  readRDS(
    paste0(data_path, "scc_sector_hourly_open_df.rds")
  )

scc_places_hourly_open_imputed_df <- 
  impute_open_hours(
    scc_places_hourly_open_raw_df, 
    scc_sector_hourly_open_df, 
    scc_places_df
  )

saveRDS(
  scc_places_hourly_open_imputed_df,
  paste0(data_path, "scc_places_hourly_open_imputed_df.rds")
)
```


# Preprocess Hourly Visit Data

## Load and join 2019 and 2020 hourly data
```{r}
scc_places_df <- 
  readRDS(
    paste0(data_path, "scc_places_df.rds")
  )

scc_places_hourly_open_imputed_df <- 
  readRDS(
    paste0(data_path, "scc_places_hourly_open_imputed_df.rds")
  )

scc_hourly_2019_df <- 
  load_hourly_scc_df(get_2019_week_start_dates(), scc_places_df) %>% 
  join_hourly_with_place_open(., scc_places_df, scc_places_hourly_open_imputed_df)

scc_hourly_2020_df <- 
  load_hourly_scc_df(get_2020_week_start_dates(), scc_places_df) %>% 
  join_hourly_with_place_open(., scc_places_df, scc_places_hourly_open_imputed_df)

scc_places_df %>% group_by(type) %>% summarize(n())
```


```{r}
scc_hourly_2019_df %>% 
  select(safegraph_place_id, type) %>% 
  unique() %>% 
  group_by(type) %>% 
  summarize(n())

scc_hourly_2020_df %>% 
  select(safegraph_place_id, type) %>% 
  unique() %>% 
  group_by(type) %>% 
  summarize(n())
```


## Filter 2019 and 2020 data to common POIs
```{r}
common_place_ids <- 
  intersect(
    scc_hourly_2019_df$safegraph_place_id, 
    scc_hourly_2020_df$safegraph_place_id
  )

scc_hourly_common_2019_df <- 
  scc_hourly_2019_df %>% filter(safegraph_place_id %in% common_place_ids)

scc_hourly_common_2020_df <- 
  scc_hourly_2020_df %>% filter(safegraph_place_id %in% common_place_ids)

scc_hourly_common_2019_df %>% 
  select(safegraph_place_id, type) %>% 
  unique() %>% 
  group_by(type) %>% 
  summarize(n())

scc_hourly_common_2020_df %>% 
  select(safegraph_place_id, type) %>% 
  unique() %>% 
  group_by(type) %>% 
  summarize(n())

saveRDS(
  scc_hourly_common_2019_df,
  paste0(data_path, "scc_hourly_common_2019_df.rds")
)

saveRDS(
  scc_hourly_common_2020_df,
  paste0(data_path, "scc_hourly_common_2020_df.rds")
)
```

## Smear 2019 and 2020 hourly data
```{r}
scc_hourly_common_2019_df <- 
  readRDS(
    paste0(data_path, "scc_hourly_common_2019_df.rds")
  )

scc_hourly_common_2020_df <- 
  readRDS(
    paste0(data_path, "scc_hourly_common_2020_df.rds")
  )

smeared_2019_df <- 
  scc_hourly_common_2019_df %>% 
  truncate_hourly_outliers() %>% 
  add_utc_hour() %>% 
  lag_median_dwell_to_utc_boundary() %>% 
  filter(!(date %in% (dst_days %>% lubridate::ymd()) & hour <= 3)) %>% 
  smear_hourly_visits() %>% 
  apply_dwell_correction_factor()

smeared_2020_df <- 
  scc_hourly_common_2020_df %>% 
  truncate_hourly_outliers() %>% 
  add_utc_hour() %>% 
  lag_median_dwell_to_utc_boundary() %>% 
  filter(!(date %in% (dst_days %>% lubridate::ymd()) & hour <= 3)) %>% 
  smear_hourly_visits() %>% 
  apply_dwell_correction_factor()
```


## Compute fraction of maximum occupancy for each hour
```{r}
scc_preprocessed_2019_df <- 
  smeared_2019_df %>% 
  mutate(
    max_occupancy = area_square_feet / MERCANTILE_OCCUPANCY_LOAD,
    occupancy_ratio = avg_hourly_visits / max_occupancy
  )

scc_preprocessed_2020_df <- 
  smeared_2020_df %>% 
  mutate(
    max_occupancy = area_square_feet / MERCANTILE_OCCUPANCY_LOAD,
    occupancy_ratio = avg_hourly_visits / max_occupancy
  )

saveRDS(
  scc_preprocessed_2019_df,
  paste0(data_path, "scc_preprocessed_2019_df.rds")
)

saveRDS(
  scc_preprocessed_2020_df,
  paste0(data_path, "scc_preprocessed_2020_df.rds")
)
```


# Academic and SCC capacity limit

## Load baseline visit data
```{r}
scc_places_df <- 
  readRDS(
    paste0(data_path, "scc_places_df.rds")
  )

scc_places_hourly_open_imputed_df <- 
  readRDS(
    paste0(data_path, "scc_places_hourly_open_imputed_df.rds")
  )

scc_hourly_baseline_df <- 
  load_hourly_scc_df(get_baseline_week_start_dates(), scc_places_df) %>% 
  join_hourly_with_place_open(., scc_places_df, scc_places_hourly_open_imputed_df)
```


## Apply smear operation to baseline period
```{r}
smeared_baseline_df <- 
  scc_hourly_baseline_df %>% 
  truncate_hourly_outliers() %>% 
  add_utc_hour() %>% 
  lag_median_dwell_to_utc_boundary() %>% 
  filter(!(date %in% (dst_days %>% lubridate::ymd()) & hour <= 3)) %>% 
  smear_hourly_visits() %>% 
  apply_dwell_correction_factor()

saveRDS(
  smeared_baseline_df,
  paste0(data_path, "smeared_baseline_df.rds")
)
```


## Compute academic and SCC capacity limit
```{r}
academic_capacity_limit_df <- 
  smeared_baseline_df %>% 
  filter(
    date >= academic_baseline_start_date & date <= academic_baseline_end_date
  ) %>% 
  group_by(safegraph_place_id, type) %>% 
  summarize(academic_max_occupancy = max(hourly_visits_smeared)) %>% 
  mutate(academic_capacity_limit = 0.2 * academic_max_occupancy)

scc_capacity_limit_df <- 
  scc_places_df %>% 
  mutate(
      scc_max_occupancy = (gross_to_net_scale * area_square_feet) / MERCANTILE_OCCUPANCY_LOAD,
      scc_capacity_limit = 0.2 * scc_max_occupancy
  ) %>% 
  select("safegraph_place_id", "scc_max_occupancy", "scc_capacity_limit", "type")

scc_capacity_limit_df <- 
  inner_join(
    academic_capacity_limit_df, 
    scc_capacity_limit_df,
  ) 

saveRDS(
  scc_capacity_limit_df,
  paste0(repo_path, output_data_dir, "scc_capacity_limit_df.rds")
)
```


# Mobility-case growth correlation cleaning

## Load case counts by county by month
```{r}
case_count_df <- 
  read_csv(nytimes_case_path) %>%
  mutate(
    year=year(date),
    month=month(date),
    week=date %>% strftime("%V")
  )
```


## Load Safegraph social distancing metrics
```{r}
social_distancing_20 <- readRDS(social_distancing_path_20)
social_distancing_21 <- readRDS(social_distancing_path_21)

social_distancing_df <- 
  rbind(social_distancing_20, social_distancing_21) %>%
  select(
    origin_census_block_group,
    date_range_start,
    date_range_end,
    device_count, 
    distance_traveled_from_home,
    median_non_home_dwell_time
  ) 
```


## Cleaning and merging data
```{r}
# Map cbg to county and compute a weighted average of dwell time
county_social_distancing_df <- 
  social_distancing_df %>%
  drop_na() %>%
  mutate(
    fips = substr(origin_census_block_group, 1, 5),
    weighted_dwell_time = device_count * median_non_home_dwell_time,
    weighted_distance = device_count * distance_traveled_from_home
  ) %>% 
  group_by(
    fips,
    date_range_start,
    date_range_end
  ) %>%
  summarize(
    cbgs = n_distinct(origin_census_block_group),
    total_devices = sum(device_count),
    weighted_average_dwell_time = sum(weighted_dwell_time) / total_devices,
    weighted_average_distance = sum(weighted_distance) / total_devices
  ) %>%
  mutate(date = as.Date(date_range_start))

## Combining data
combined_data_df <- 
  county_social_distancing_df %>%
  left_join(case_count_df, by = c("date","fips")) 

saveRDS(
  combined_data_df,
  paste0(repo_path, output_data_dir, "bay_area_case_distancing.rds")
)
```


## Creating the baseline distance
```{r}
combined_data_df <- 
  readRDS(
    paste0(repo_path, output_data_dir, "bay_area_case_distancing.rds")
  )

baseline_df <- 
  combined_data_df %>%
  filter(date <= '2020-01-31' && date > '2020-01-07') %>%
  mutate(wday = lubridate::wday(date)) %>% 
  group_by(fips, wday) %>%
  summarize(
    baseline_dwell_time = mean(weighted_average_dwell_time),
    baseline_distance = mean(weighted_average_distance)
  )
```


```{r}
#Putting it together
analysis_data_df <- 
  combined_data_df %>%
  mutate(wday = lubridate::wday(date)) %>% 
  filter(date > '2020-02-29' && date < '2021-03-01') %>%
  left_join(baseline_df, by = c("fips", "wday")) %>%
  mutate(
    dwell_ratio = weighted_average_dwell_time / baseline_dwell_time,
    distance_ratio = weighted_average_distance / baseline_distance  
  ) %>% 
  ungroup() %>% 
  select(fips, date, county, cases, dwell_ratio, distance_ratio) %>% 
  filter(!is.na(county))

growth_data_df <- 
  analysis_data_df %>% 
  group_by(county) %>%
  arrange(date, .by_group = TRUE) %>% 
  nest() %>%
  mutate(
    roll_diff = map(
      data,
      ~ .x %>% mutate(
          new_cases = slider::slide_dbl(
            ., ~ .x$cases[2] - .x$cases[1], .before = 1),
          mean_dwell_ratio_7 = slider::slide_dbl(
            ., ~ mean(.x$dwell_ratio), .before = 3, .after= 3, .complete = TRUE)
      )
    )
  ) %>% 
  select(-data) %>% 
  unnest(roll_diff) %>% 
  group_by(county) %>% 
  arrange(date, .by_group = TRUE) %>% 
  nest() %>% 
  mutate(
    roll_sum = map(
      data, 
      ~ .x %>% mutate(
        log_sum_3 = slider::slide_dbl(
          ., ~ log(sum(.x$new_cases / 3)), .before = 2, .complete = TRUE),
        log_sum_7 = slider::slide_dbl(
          ., ~ log(sum(.x$new_cases / 7)), .before = 6, .complete = TRUE),
        log_sum_14 = slider::slide_dbl(
          ., ~ log(sum(.x$new_cases / 14)), .before = 13, .complete = TRUE),
        mean_new_cases_7 = slider::slide_dbl(
          ., ~ mean(.x$new_cases), .before = 6),
      )
    )
  ) %>%
  select(-data) %>% 
  unnest(roll_sum) %>% 
  mutate(
    case_growth = log_sum_3 / (log_sum_7 + 1e-15),
    case_growth_alt = log_sum_7 / (log_sum_14 + 1e-15)
  )

prior_ratio_df <- 
  growth_data_df %>%
  mutate(
    dummy_date = date + 11,
    mobility_dwell_ratio = dwell_ratio,
  ) %>%
  select(
    dummy_date, 
    mobility_dwell_ratio,
    mean_dwell_ratio_7,
    fips
  ) %>%
  rename(date = dummy_date)

lagged_analysis_data_df <- 
  growth_data_df %>%
  select(
    -c(
      dwell_ratio,
      distance_ratio, 
      mean_dwell_ratio_7,
    )
  ) %>% 
  left_join(prior_ratio_df, by = c("date","fips", "county")) %>%
  drop_na() %>%
  select(
    county, 
    new_cases, 
    cases, 
    mean_new_cases_7,
    case_growth, 
    case_growth_alt,
    mobility_dwell_ratio,
    mean_dwell_ratio_7,
    date
  ) %>%
  mutate(month_yr = format(as.Date(date), "%Y-%m"))

saveRDS(
  lagged_analysis_data_df,
  paste0(repo_path, output_data_dir, "lagged_analysis_data_df.rds")
)
```


```{r}
correlations_df <- 
  lagged_analysis_data_df %>% 
  group_by(county) %>%
  arrange(date, .by_group = TRUE) %>% 
  nest() %>%
  mutate(
    roll_cor = map(
      data, 
      ~ .x %>% mutate(
        dwell_corr = slider::slide_dbl(
          ., 
          ~ cor.test(.x$case_growth, .x$mean_dwell_ratio_7, method = "pearson")[4]$estimate, 
          .before = 27, 
          .complete = TRUE),
        dwell_lower_bound = slider::slide_dbl(
          ., 
          ~ cor.test(.x$case_growth, .x$mean_dwell_ratio_7, method = "pearson")$conf.int[1], 
          .before = 27, 
          .complete = TRUE),
        dwell_upper_bound = slider::slide_dbl(
          ., 
          ~ cor.test(.x$case_growth, .x$mean_dwell_ratio_7, method = "pearson")$conf.int[2], 
          .before = 27, 
          .complete = TRUE),
        dwell_corr_alt = slider::slide_dbl(
          ., 
          ~ cor.test(.x$case_growth_alt, .x$mean_dwell_ratio_7, method = "pearson")[4]$estimate, 
          .before = 27, 
          .complete = TRUE),
        dwell_lower_bound_alt = slider::slide_dbl(
          ., 
          ~ cor.test(.x$case_growth_alt, .x$mean_dwell_ratio_7, method = "pearson")$conf.int[1], 
          .before = 27, 
          .complete = TRUE),
        dwell_upper_bound_alt = slider::slide_dbl(
          ., 
          ~ cor.test(.x$case_growth_alt, .x$mean_dwell_ratio_7, method = "pearson")$conf.int[2], 
          .before = 27, 
          .complete = TRUE)
      )
    )
  ) %>%
  select(-data) %>% 
  unnest(roll_cor)

saveRDS(
  correlations_df,
  paste0(repo_path, output_data_dir, "correlations_df.rds")
)
```

